### 2023-01-24 Strydom_et_al_2023_graph_embedding_draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@2a1f16b72dc7d9c83e6211b0433d8904ab134298 🚀

\begin{enumerate}
    \itemMetawebs, (networks of potential interactions within a species
pool) are a powerful abstraction to understand how large-scale species
interaction networks are structured.%
    \itemBecause metawebs are typically expressed at large spatial and
taxonomic scales, assembling them is a tedious and costly process;
predictive methods can help circumvent the limitations in data
deficiencies, by providing `draft' metawebs.%
    \itemOne way to improve our ability to predict metawebs is to
maximize available information by using graph embeddings, instead of the
list of species interactions. Graph embedding is an emerging field in
machine learning that holds great potential for ecological problems.%
    \itemIn this perspective, we outline how the challenges associated
with inferring metawebs line-up with the advantages of graph embeddings;
as well as discuss how the choice of the species pool has consequences
on the reconstructed network, but also embeds hypotheses about which
human-made boundaries are ecologically meaningful.%
\end{enumerate}

>>>>

\begin{enumerate}
    \item Metawebs, (networks of potential interactions within a species
pool) are a powerful abstraction to understand how large-scale species
interaction networks are structured.%
    \item Because metawebs are typically expressed at large spatial and
taxonomic scales, assembling them is a tedious and costly process;
predictive methods can help circumvent the limitations in data
deficiencies, by providing `draft' metawebs.%
    \item One way to improve our ability to predict metawebs is to
maximize available information by using graph embeddings, instead of the
list of species interactions. Graph embedding is an emerging field in
machine learning that holds great potential for ecological problems.%
    \item In this perspective, we outline how the challenges associated
with inferring metawebs line-up with the advantages of graph embeddings;
as well as discuss how the choice of the species pool has consequences
on the reconstructed network, but also embeds hypotheses about which
human-made boundaries are ecologically meaningful.%
\end{enumerate}
